### 2014-08-07 paper/paper.tex
Made a change to the links in the two readmes
Made the reccomended changes. Still a few more to go

August 4th, 2014 %TODO fix this

@@

Draft 4 %TODO ditch this

@@

% TODO expand on IIS

@@

The \textit{Precision} measure for the positive label is $P_{pos} =
\frac{\mathrm{\# of\ true\ postive}}{\mathrm{\# of\ true\ postive} + \mathrm{\#
of\ false\ postive} }$. The \textit{Recall} measure for the positive label is
defined as $R_{pos} = \frac{\mathrm{\# of\ true\ postive}}{\mathrm{\# of\ true\
postive} + \mathrm{\# of\ false\ negative} }$. $P_{neg}$ and $R_{neg}$ can be
calculated in a similar fashion.

@@

            %TODO is this clear?

@@

@@

\begin{table}[H]
    \begin{center}
    \begin{tabular}{|c||r|r|r|r|}
        \hline
        Description        & Positive & Neutral & Negative & Overall \\
        \hline
        All                & 14.85    & 14.06   & 15.10    & 14.49 \\
        Just Stopwords     & 17.13    & 16.86   & 17.41    & 17.04 \\
        Just Uncommon      & 18.43    & 17.87   & 18.85    & 18.21 \\
        Just Normalization & 19.65    & 19.16   & 20.06    & 19.46 \\
        Baseline           & 20.65    & 20.45   & 20.96    & 20.58 \\
        \hline
    \end{tabular}
    \end{center}
    \caption{`Positive', `Neutral', `Negative', and `Overall' refer to the
    average number of features per Tweet in each experiment.}
    \label{table:numfeatures}
\end{table}

%TODO check these results

@@

\begin{table}[H]
    \begin{center}
    \begin{tabular}{|r||c|c|c|}
        \hline
        Description    & $\mu F$ & $\sigma F$ & $\delta\ \mu F$ \\
        \hline
        All            & \textbf{50.96} & 1.93 &  2.59 \\
        Just Stopwords & 48.27   & 1.83 & -0.10 \\
        Just Uncommon  & 49.02   & 1.96 &  0.65 \\
        Just Normalize & 49.55   & 2.10 &  1.18 \\
        Baseline       & 48.37   & 2.15 & - \\
        \hline
    \end{tabular}
    \end{center}
    \caption{Performance of the Maximum Entropy classifier using exhaustive
    cross-validation with 5 partitions}
    \label{table:maxent-results}
\end{table}

@@

\begin{table}[H]
    \begin{center}
    \begin{tabular}{|r||c|c|c|}
        \hline
        Description    & $\mu F$ & $\sigma F$ & $\delta\ \mu F$ \\
        \hline
        All            & 49.28  & 0.81 &  1.17 \\
        Just Stopwords & 47.29  & 0.76 & -0.82 \\
        Just Uncommon  & 48.34  & 1.11 &  0.23 \\
        Just Normalize & \textbf{49.44} & 1.00 & 1.33\\
        Baseline       & 48.11  & 0.74 & - \\
        \hline
    \end{tabular}
    \end{center}
    \caption{Performance of the Naive Bayes classifier using exhaustive
    cross-validation with 5 partitions}
    \label{table:bayes-results}
\end{table}

@@

% TODO Student T-test

@@

    \item \textbf{Download Source} - The source code is hosted on github.com
        and can be viewed there
        \footnote{https://github.com/hockeybuggy/twitter-sentiment}. To download a
        zip file and open it:

@@

% TODO test this and make a dist branch

>>>>

August 7th, 2014 %TODO fix this

@@

Draft 5 %TODO ditch this

@@

@@

The \textit{Precision} measure for the positive label is $P_{pos} =
\frac{\mathrm{\# of\ true\ positive}}{\mathrm{\# of\ true\ positive} + \mathrm{\#
of\ false\ positive} }$. The \textit{Recall} measure for the positive label is
defined as $R_{pos} = \frac{\mathrm{\# of\ true\ positive}}{\mathrm{\# of\ true\
positive} + \mathrm{\# of\ false\ negative} }$. $P_{neg}$ and $R_{neg}$ can be
calculated in a similar fashion.

Accuracy is used as a secondary performance measure. While more intuitive, it
is not used as a primary evaluation measure due to it's tendency to be biased
by uneven numbers of examples particular labels in the dataset. Accuracy,
henceforth referred to as $Acc$, can be calculate with the following formula:

\begin{equation}
    Acc = \frac{\mathrm{\# of\ true\ positive} + \mathrm{\# of\ true\ negative}}{N}
\end{equation}

Where $N$ is equal to the total number of documents in the \textit{test set}.

@@

@@

%TODO change the label names

@@

\begin{table}[H]
    \begin{center}
    \begin{tabular}{|r||c|c|c|c|}
        \hline
        Description        & Positive & Neutral & Negative & Overall \\
        \hline
        Baseline           & 20.65    & 20.45   & 20.96    & 20.58 \\
        Just Stopwords     & 17.13    & 16.86   & 17.41    & 17.04 \\
        Just Uncommon      & 18.43    & 17.87   & 18.85    & 18.21 \\
        Just Normalization & 19.65    & 19.16   & 20.06    & 19.46 \\
        All                & 14.85    & 14.06   & 15.10    & 14.49 \\
        \hline
    \end{tabular}
    \end{center}
    \caption{`Positive', `Neutral', `Negative', and `Overall' refer to the
    average number of features per Tweet in each experiment.}
    \label{table:numfeatures}
\end{table}

@@

%TODO finish accuracy

\begin{table}[H]
    \begin{center}
    \begin{tabular}{|r||c|c|c|c|c|}
        \hline
        Description    & $\mu F$ & $\sigma F$ & $\delta\ \mu F$ & $\mu Acc$ & $\sigma Acc$ \\
        \hline
        Baseline       & 48.37   & 2.15 & -     & & \\
        Just Stopwords & 48.27   & 1.83 & -0.10 & 62.07 & 1.69 \\
        Just Uncommon  & 49.02   & 1.96 &  0.65 & 62.47 & 1.91 \\
        Just Normalize & 49.55   & 2.10 &  1.18 & 63.57 & 1.75 \\
        All            & \textbf{50.96} & 1.93 &  2.59 & \textbf{63.82} & 0.91 \\
        \hline
    \end{tabular}
    \end{center}
    \caption{Performance of the Maximum Entropy classifier using exhaustive
    cross-validation with 5 partitions}
    \label{table:maxent-results}
\end{table}

@@

%TODO finish table

\begin{table}[H]
    \begin{center}
    \begin{tabular}{|r||c|c|c|c|c|}
        \hline
        Description    & $\mu F$ & $\sigma F$ & $\delta\ \mu F$ & $\mu Acc$ & $\sigma Acc$ \\
        \hline
        Baseline       & 48.11  & 0.74 & - & & \\
        Just Stopwords & 47.29  & 0.76 & -0.82 & & \\
        Just Uncommon  & 48.34  & 1.11 &  0.23 & & \\
        Just Normalize & \textbf{49.44} & 1.00 & 1.33 & & \\
        All            & 49.28  & 0.81 &  1.17 & & \\
        \hline
    \end{tabular}
    \end{center}
    \caption{Performance of the Naive Bayes classifier using exhaustive
    cross-validation with 5 partitions}
    \label{table:bayes-results}
\end{table}

@@

@@

    \item \textbf{Download Source} - The source code is hosted on github.com
        and can be viewed there
        \footnote{https://github.com/hockeybuggy/twitter-sentiment/tree/dist}.
        To download a zip file and open it:

@@
